%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{twentysecondcv}
\cvname{Aida Shams}
\cvjobtitle{Data and Business Analyst}
\cvlinkedin{linkedin.com/in/aida-shams-b0379577}
\cvnumberphone{+64 21 022 55679}
\cvmail{a.shams@auckland.ac.nz}

\programming{{C++ / 3},
             {SPSS / 5.2},
             {Advanced Excel / 5.8},
             {Power BI / 5.5},
             {R / 4.3},
             {Python / 4.5},
             {SQL / 5.7}}

\newcommand\skills{
    \smartdiagram[bubble diagram]{
        \textbf{Process}\\\textbf{Re-design},
        \textbf{Project}\\\textbf{Management},
        \textbf{Reports}\\\textbf{and KPIs},
        \textbf{Continuous}\\\textbf{Improvement},
        \textbf{SAP}\\\textbf{ERP},
        \textbf{Lean}\\\textbf{Philosophy}
    }
}

\about{I am Ida and I am super and cool}

\begin{document}
\makeprofile{}

\section{Experience}
\begin{twenty}
\twentyitem{2023--2023}
    {}
    {Software Engineering Lead}
    {\href{https://www.dotmatics.com/}{Dotmatics - OMIQ Team}}
    {}
    {Led major refactoring projects in Go to enhance the architectural
    efficiency of our flow cytometry software. Managed the Jira board to
    streamline team workflows and advocated for agile best practices. Conducted
    a thorough readiness audit to ensure operational resilience and secure key
    management. Actively contributed to building and training a dynamic team,
    incorporating generative AI in the hiring process for improved candidate
    selection. Proactively reviewed and improved team PRs, and consistently
    monitored and reported on KPIs to drive performance insights, despite
    limited access to metrics.
    Skills: \emph{Go, GCS, Kubernetes, Postgres, Jira, OpenTelemetry,
    Docker, Angular}} \\

\twentyitem{2022--2022}
    {}
    {Senior Engineer}
    {\href{https://www.soulmachines.com/}{Soul Machines - Platform Performance Team}}
    {}
    {Designed and implemented an OpenTelemetry distributed tracing system to
    expose performance defects in the product. Solicited buy-in from
    stakeholders and closely managed the implementation and deployment process.
    The system delivered results almost immediately and led to directly
    measurable improvements in the product.
    Skills: \emph{Agile, Jira, OpenTelemetry, GitHub, AWS, Azure, C\#,
    TypeScript, Docker, Terraform}} \\

\twentyitem{2018--2022}
    {}
    {Project Lead}
    {\href{https://sylo.io/}{Sylo - Backend Development Team}}
    {}
    {Managed the design of the Sylo Node. Also a primary architect of the Sylo
    Network. Grew and led an agile team of six people. Responsible for the full
    product development lifecycle: concept, research, implementation,
    deployment, scaling, iteration, maintenance, and support.
    Skills: \emph{Go, Jira, AWS, Flutter, Elm, JavaScript, Libp2p, GitHub,
    Protobuf}} \\

\twentyitem{2016--2018}
    {}
    {Software Researcher}
    {\href{https://pal.auckland.ac.nz/}{UoA - Physical Acoustics Laboratory}}
    {}
    {Managed the development of a modular laboratory automation framework.
    Deployed into an academic research setting as the automation system for a
    laser laboratory. Published the framework in a US physics textbook.
    Skills: \emph{Python, Elm, JavaScript, Github, C, Cython, Java, Lua}} \\

\end{twenty}

\section{Education}
\begin{twenty}
    \twentyitem{2014--2016}{}{Masters Degree | Computer Science}{\href{https://www.cs.auckland.ac.nz/en.html}{University of Auckland}}{}{First Class Honours - Artificial Intelligence}
    \twentyitem{2010--2014}{}{Bachelors Degree | Computer Science}{\href{http://eecs.oregonstate.edu/academics/undergraduates/computer-science}{Oregon State University}}{}{Summa Cum Laude}
    % \twentyitem{2008--2010}{}{Associates Degree | Graphic Design}{\href{https://www.pcc.edu/programs/graphic-design/}{Portland Community College}}{}{Highest Honors}
\end{twenty}

\end{document}
